Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-25 Paper/MSRChallenge2017.tex
added numbers to the table and performed a pass through the paper to check for typos

\begin{comment}
we have created a dataset with technical attributes to be able to analyze the 
predictive power of these attributes and its relationship with commit integration 
success. This way, we are able to create a model
We are afterwards interested in knowing if adding social attributes to this 
predictability model will increase the probability of the model asserting 
correctly future instances by knowing not only technical data about the commit 
being pushed but also social attributes of the developer pushing the changes.
\end{comment}

@@

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling. We downsampled the entire dataset being analyzed and then performed cross-validation on it. Since the cross-validation is stratified, the proportion of 50-50 is maintained through the training and testing folds. We train and present results for both
data sets individually in Sections \ref{eval}A, \ref{eval}B and \ref{eval}C.
\section{Evaluation} \label{eval}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\

\textbf{Incorrectly Classified Instances}&  22.99\% & 18.90\% & 35.90\% & 23.91\%\\

@@

 The scripts we have created to adapt and extract the datasets we needed, and the 
 scripts to obtain the developer social data are publicly available to facilitate 
 the transparency and quality of the process (Will be available after double blind review).%\footnote{https://goo.gl/CqTX44}

@@

\section{Related work:}
The most similar related work to this paper is a case study investigating how
social, technical, coordination, and prior-certification factors affect build
success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
focused on one project and measured experience as the number of contributions to
that project while our study focuses on a wide range of open source projects and
measures experience through developers' profile information.
Another study investigated the relationship between authors, files in project,
and team organization when predicting build
success on an IBM project with 151 developers.  The study found that as the
number of authors or files in a build increases, the probability of build
success decreases~\cite{Kwan11}. Another investigation used a dataset from the
same project and
found that team structures affected the teams' build success rate~\cite{Wolf09}.
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast, we focus on the relationship between independent social 
attributes and continuous integration success.

>>>>

@@

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling. We downsampled the entire dataset being analyzed and then performed cross-validation on it. Since the cross-validation is stratified, the proportion of 50-50 is maintained through the training and testing folds. We train and present results for both
data sets individually in Sections \ref{eval}A, \ref{eval}B and \ref{eval}C.
\section{Evaluation} \label{eval}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
	\textbf{Correctly Classified Instances}&  285882 (77.01\%) & 301068
	(81.10\%)  & 121694 (64.10\%) & 144441 (76.09\%)\\

	\textbf{Incorrectly Classified Instances}&  85326 (22.99\%) & 70140
	(18.90\%) & 68147 (35.90\%) &  45400 (23.91\%)\\

@@

 The scripts we have created to adapt and extract the datasets we needed, and the 
 scripts to obtain the developer social data are publicly available to facilitate 
 the transparency and quality of the process\footnote{https://goo.gl/CqTX44}.

@@

\section{Related work}
The most similar related work to this paper is a case study investigating how
social, technical, coordination, and prior-certification factors affect build
success for a project with 40 developers at IBM Toronto Labs~\cite{Hassan06}.  This work 
focused on one project and measured experience as the number of contributions to
that project while our study focuses on a wide range of open source projects and
measures experience through developers' profile information.
Another study investigated the relationship between authors, files in project,
and team organization when predicting build
success on an IBM project with 151 developers.  The study found that as the
number of authors or files in a build increases, the probability of build
success decreases~\cite{Kwan11}. A separate investigation used a dataset from the
same project and
found that team structures affected the teams' build success rate~\cite{Wolf09}.
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs. Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.
Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast with their work, we focus on the relationship between independent social 
attributes and continuous integration success.
